```{r library and data}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(bayesrules)
library(bayesplot)
library(rstanarm)

drug_data <- read.csv("../data/drugs.csv")


#filtering for age ranges and 5 biggest states by population
alc_dis_rate_1217 <- drug_data %>% 
  select(
    state = State, 
    alc_dis_rate   = `Rates.Alcohol.Use.Disorder.Past.Year.12.17`,
  ) %>% 
  filter(state %in% c("California", "Texas", "Florida", "New York", "Pennsylvania"))

alc_dis_rate_1825 <- drug_data %>% 
  select(
    state = State, 
    alc_dis_rate   = `Rates.Alcohol.Use.Disorder.Past.Year.18.25`,
  ) %>% 
  filter(state %in% c("California", "Texas", "Florida", "New York", "Pennsylvania"))

alc_dis_rate_26 <- drug_data %>% 
  select(
    state = State, 
    alc_dis_rate   = `Rates.Alcohol.Use.Disorder.Past.Year.26.`,
  ) %>% 
  filter(state %in% c("California", "Texas", "Florida", "New York", "Pennsylvania"))
```

---
title: "Stats 115 Final Presentation: Drug Use in Young Adults"
author: "Group 14: Melody Fang, Andrew Liu, Hasnain Sizar, Tyler Tran"
format: 
  revealjs: 
      theme: moon
      width: 1400
      margin: 0.05
      center: false
---

## Data Description


## Problem/Question Description
- Across different age groups, which state (out of the top 5 with the highest populations in the United States) has the highest rate of alcohol usage disorder?
- Which age group has the overall highest rate?

## Prior Description

- **Weakly informative priors**
- Rate is measured **per 1,000**
- Age pattern: **12--17 < 26+ < 18--25**
- **All 50 states** → hierarchical model with **partial pooling**

**Intercept priors**

- `12--17: normal(30, 15)`

- `18--25: normal(140, 30)`

- `26+: normal(60, 20)`

**Other priors**

- `aux: exponential(1)`

- `cov: decov(1, 1, 1, 1)`

## Age Group 1: 12-17 {.nostretch}
:::: {.columns}

::: {.column width="40%"}
```{r AG1 plots}
mean_rate <- mean(alc_dis_rate_1217$alc_dis_rate)
ggplot(alc_dis_rate_1217, aes(x = state, y = alc_dis_rate)) +
  geom_boxplot() +
  labs(title = "Alcohol Disorder Rate for Age Range 12-17", x = "State", y = "Alcohol Disorder Rate") + geom_hline(yintercept = mean_rate, color = "red", linetype = "solid")
```
:::

::: {.column width="60%"}
yap
:::

::::

## Age Group 2: 18-25
:::: {.columns}

::: {.column width="40%"}
```{r AG2 plots}
mean_rate <- mean(alc_dis_rate_1825$alc_dis_rate)
ggplot(alc_dis_rate_1825, aes(x = state, y = alc_dis_rate)) +
  geom_boxplot() +
  labs(title = "Alcohol Disorder Rate for Age Range 18-25", x = "State", y = "Alcohol Disorder Rate") + geom_hline(yintercept = mean_rate, color = "red", linetype = "solid")
```
:::

::: {.column width="60%"}
yap
:::

::::

## Age Group 3: 26+
:::: {.columns}

::: {.column width="40%"}
```{r AG3 plots}
mean_rate <- mean(alc_dis_rate_26$alc_dis_rate)
ggplot(alc_dis_rate_26, aes(x = state, y = alc_dis_rate)) +
  geom_boxplot() +
  labs(title = "Alcohol Disorder Rate for Age Range 26+", x = "State", y = "Alcohol Disorder Rate") + geom_hline(yintercept = mean_rate, color = "red", linetype = "solid")
```
:::

::: {.column width="60%"}
yap
:::

::::

## Age Group Comparison


## Analysis & Conclusion