```{r library and data}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(bayesrules)
library(bayesplot)
library(rstanarm)

drug_data <- read.csv("data/drugs.csv")
```

---
title: "Stats 115 Final Presentation: Drug Use in Young Adults"
author: "Group 14: Melody Fang, Andrew Liu, Hasnain Sizar, Tyler Tran"
format: 
  revealjs: 
      theme: moon
---

## Data Description


## Problem/Question Description
- Across different age groups, which state (out of the top 5 with the highest populations in the United States) has the highest rate of alcohol usage disorder?
- Which age group has the overall highest rate?

## Prior Description


## Age Group 1: 12-17 {.nostretch}
:::: {.columns}

::: {.column width="40%"}
yap
:::

::: {.column width="60%"}
```{r AG1}
alc_dis_rate_1825 <- drug_data %>% 
  select( state = State,alc_dis_rate   = `Rates.Alcohol.Use.Disorder.Past.Year.18.25`,
  ) %>% filter(state %in% c("California", "Texas", "Florida", "New York", "Pennsylvania"))

mean_rate <- mean(alc_dis_rate_1825$alc_dis_rate)
ggplot(alc_dis_rate_1825, aes(x = state, y = alc_dis_rate)) +
  geom_boxplot() +
  labs(title = "Alcohol Disorder Rate for Age Range 18-25", x = "State", y = "Alcohol Disorder Rate") + geom_hline(yintercept = mean_rate, color = "red", linetype = "solid")
```
:::

::::

## Age Group 2: 18-25

## Age Group 3: 26+

## Age Group Comparison


## Analysis & Conclusion